Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-28 snapshot_system/snapshot.tex
analysis

\subsection{Popular Chunk Management and VM-oriented Fault Isolation}

Our objective for fault isolation is to minimize the number of VMs affected when there are failures
in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
for each VM is localized within the parent and the current snapshot.
Thus there is no data dependence between VMs.
For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
of shared blocks by adding extra replcas of those shared blocks.

@@

{\bf Fault resilence.}

>>>>

\subsection{Popular Chunk Management and VM-oriented Fault Isolation}
Our objective for fault isolation is to minimize the number of VMs affected when there are failures
in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
for each VM is localized within the parent and the current snapshot.
Thus there is no data dependence between VMs.
For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
of shared blocks by adding extra replcas of those shared blocks.

@@
